Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
begin mark phase

% Points to make
%
% (1) Lets operators think about topologies/policies at a high-level of abstraction
%     - matches current thinking (e.g., templates)
%
% (2) Promotes a correct-by-construction methodology
%
%     properties that hold over abstract topologies hold over concrete ones
%      - includes correct forwarding behavior
%      - includes reachability (under k-failures)
%
% (3) Enables reusability (e.g., across datacenters) and expansion (e.g., within a datacenter)
%
% (4) lets us scale synthesis to large-scale topologies

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=1.02\columnwidth]{figures/templates}
  \caption{Example of a small part of a router template for the datacenter spine role.}
  \label{fig:example2}
  \vspace{-1em}
\end{figure}

@@

To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
The network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Templates have parameters for various aspects of the configuration (\EG, neighbor list) and are compiled to device configurations by instantiating the parameters using the network topology and a database of network information.
\ryan{TODO: discuss figure}

>>>>

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/templates}
  \caption{Example of a small configuration component of a router template for the datacenter spine role.}
  \label{fig:templates}
  \vspace{-1em}
\end{figure}

@@

To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two datacenters might look like. The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and are compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.
